Case study validations of automatic bullet matching

### 2018-11-14 index.Rmd
error rates and percentages
Define wrong/missed identifications.

@@

## Identification Errors
\svp{XXX define wrong identification and missed identification here XXX}

>>>>

## Identification Errors
\svp{XXX define wrong identification and missed identification here XXX}
\svp{When evaluating algorithm performance, it is useful to distinguish between two types of errors, which we will refer to as \textbf{wrong identification} and \textbf{missed identification} in this paper. Wrong identifications are those in which two bullets from different sources are determined to be from the same source. Missed identifications are those in which two bullets from the same source are determined to be from different sources.}
\svp{XXX Relate to AFTE Theory of Examination criteria? How to handle ``inconclusive"?}

@@
